---
title: "TeeJet Research"
output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE, warning = FALSE}
library(flexdashboard)
library(tidyverse)
library(ggthemes)
library(plotly)
library(shiny)
library(reactable)
library(reactablefmtr)
library(ggrepel)
library(ggfittext)
```



```{r warning = FALSE, echo=FALSE}
# Dados
readxl::read_excel("shopping_price.xlsx") -> data
read_csv("names.csv") -> data1
read_csv("dados_completos.csv") |> 
    filter(!group %in% c("7", "8")) -> data_cb
read_csv("diff_price.csv") -> diff_price
```



# Brazil price comparison  

## Inputs {.sidebar}

```{r}
selectInput("select1", label = h4("Category"), 
    choices = unique(data_cb$group), selected = 1)

selectInput("select2", label = h4("Year"),
              choices =  unique(data_cb$ano), selected = "2021")
```



## Column {data-width="500"}

### Data

```{r}
renderPlotly({
data_cb |> 
  filter(group == input$select1 & ano == input$select2) |> 
  ggplot(aes(x = pontas, y = price, color = regiao)) +
  geom_boxplot(color = "#333333") +
  geom_jitter(size = 2, alpha = 0.3) +
  coord_flip() +
  labs(color = NULL) +
  scale_color_brewer(palette = "Set1") +
  theme_fivethirtyeight() +
    theme(legend.position = "none")
})
```

### Price difference by year (2021 - 2022)

```{r}
renderReactable({
data_cb |> 
  filter(group == input$select1) |> 
  group_by(pontas, group, ano) |> 
  summarise(price_mean = round(mean(price),2)) |> 
  pivot_wider(names_from = ano, values_from = price_mean) |> 
  mutate(perc = round((`2022` - `2021`) / `2022` * 100,0)) |> 
  ungroup() |> 
  dplyr::select(pontas, `2021`, `2022`, perc) -> tab2

tab2 |> 
  reactable(pagination = FALSE,
              theme = nytimes(font_size = 13, header_font_size = 15),
              resizable = TRUE,
              wrap = TRUE,
            columns = list(
              pontas = colDef(name = "Spray tip", align = "center"),
              perc = colDef(name = "Difference (%)", align = "center",
                            cell = data_bars_pos_neg(tab2, 
                                                     colors = c("#ff3030", "#1e90ff")))))
})
```

## Column {data-width="500"}




### Price and Comparison with TeeJet

```{r}
renderReactable({
diff_price |> 
  filter(group == input$select1 & ano == input$select2) |> 
  dplyr::select(pontas, preco_medio, sd, diff) -> tab1
  
tab1 |> 
  reactable(pagination = FALSE,
              theme = nytimes(font_size = 13, header_font_size = 15),
              resizable = TRUE,
              wrap = TRUE,
            columns = list(
              pontas = colDef(name = "Spray tip", align = "center"), 
              preco_medio = colDef(name = "Price (RS$)", align = "center",
                                   cell = color_tiles(tab1, colors = 
                                                         c("#FF0000",
                                                           "#7FFFD4"))),
              sd = colDef(name = "SD", align = "center"), 
              diff = colDef(name = "Difference (%)", align = "center",
              cell = data_bars_pos_neg(tab1, colors = c("#ff3030", "#1e90ff")))))
})
```




### Price comparison (Online vs TeeJet Research)

```{r}
renderPlotly({
data_cb |> 
  filter(group == input$select1 & ano == input$select2) |> 
  mutate(online = case_when(
    regiao == "Online" ~ TRUE,
    TRUE ~ FALSE
  )) |> 
  group_by(pontas, group, ano, online) |> 
  summarise(price_mean = round(mean(price),2), sd = round(sd(price),2)) |> 
  ggplot(aes(x = pontas, y = price_mean, color = online)) +
  geom_point(size = 3, 
             position = position_dodge2(width = 0.7),
             show.legend = FALSE) +
  geom_linerange(aes(ymin = price_mean - sd, 
                     ymax = price_mean + sd),
                 position = position_dodge2(width = 0.7)) +
  coord_flip() +
  theme_fivethirtyeight() + 
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none")
})
```


# Brazilian states



## Column {data-width="500"}

### Price comparison by state

```{r}
renderPlotly({
data_cb |> 
  group_by(regiao, pontas, group, ano) |> 
  summarise(price = round(mean(price),2)) |> 
  filter(group == input$select1 & ano == input$select2) |> 
  ggplot(aes(x = pontas, y = price, fill = regiao)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_brewer(palette = "Set1") +
  labs(fill = NULL) +
  theme_fivethirtyeight()
})
```

### Demographics

```{r}
renderPlotly({
data_cb |> 
  count(group, regiao, ano) |> 
  filter(group == input$select1 & ano == input$select2) |> 
  ggplot(aes(x = fct_reorder(regiao, n), y = n, fill = regiao, label = n)) +
  geom_col() + 
  coord_flip() +
  theme_fivethirtyeight() +
  scale_fill_brewer(palette = "Set1") +
  geom_bar_text(position = "stack", reflow = TRUE) +
  theme(legend.position = "none")
})
```

## Column {data-width="500"}

### Map of Brazil

```{r}
renderPlotly({
geobr::read_state() -> estado
data_cb |> 
  count(estado, ano, group) |> 
  right_join(estado, by = c("estado" = "abbrev_state")) |> 
  sf::st_as_sf() -> estado1

estado1 |> 
  filter(group == input$select1 & ano == input$select2) |> 
  ggplot() +
  geom_sf(data = estado) +
  geom_sf(aes(fill = n)) +
  scale_fill_viridis_c(option = "H") +
  theme_map() +
  labs(fill = NULL)
})
```




# AIXR and TT combined

## Inputs {.sidebar}

```{r}
selectInput("select3", label = h4("Year"),
              choices =  unique(data_cb$ano), selected = "2021")
```



## Column {data-width="500"}

### Data

```{r}
renderPlotly({
data_cb |> 
  filter(group %in% c(3,5)) |> 
  filter(ano == input$select3) |> 
  ggplot(aes(x = pontas, y = price, color = regiao)) +
  geom_boxplot(color = "#333333") +
  geom_jitter(size = 2, alpha = 0.3) +
  coord_flip() +
  labs(color = NULL) +
  scale_color_brewer(palette = "Set1") +
  theme_fivethirtyeight() +
    theme(legend.position = "none")
})
```



## Column {data-width="500"}




### Price and Comparison with TeeJet

```{r}
renderReactable({
data_cb |> 
  filter(group %in% c(3,5)) |>
  group_by(pontas, ano, manufacturer) |> 
  summarise(preco_medio = round(mean(price),2), sd = round(sd(price),2)) |> 
  ungroup(pontas, ano, manufacturer) |> 
  mutate(preco_base = case_when(
    pontas == "TT-VP" ~ preco_medio,
    TRUE ~ NA_real_)) |> 
  arrange(ano, desc(preco_medio)) |> 
  fill(preco_base, .direction = "up") |> 
  mutate(diff = round((preco_medio - preco_base) / preco_base * 100,1)) |> 
  filter(ano == input$select3) |> 
  dplyr::select(pontas, preco_medio, sd, diff) -> tab1
  
tab1 |> 
  reactable(pagination = FALSE,
              theme = nytimes(font_size = 13, header_font_size = 15),
              resizable = TRUE,
              wrap = TRUE,
            columns = list(
              pontas = colDef(name = "Spray tip", align = "center"), 
              preco_medio = colDef(name = "Price (RS$)", align = "center",
                                   cell = color_tiles(tab1, colors = 
                                                         c("#FF0000",
                                                           "#7FFFD4"))),
              sd = colDef(name = "SD", align = "center"), 
              diff = colDef(name = "Difference (%)", align = "center",
              cell = data_bars_pos_neg(tab1, colors = c("#ff3030", "#1e90ff")))))
})
```


# XR-VK vs all spray tips 

## Inputs {.sidebar}

```{r}
selectInput("select4", label = h4("Year"),
              choices =  unique(data_cb$ano), selected = "2021")
```




## Column {data-width="500"}

```{r}
renderReactable({
data_cb |> 
  group_by(pontas, ano, manufacturer) |> 
  summarise(preco_medio = round(mean(price),2), sd = round(sd(price),2)) |> 
  ungroup(pontas,  ano, manufacturer) |> 
  mutate(preco_base = case_when(
    pontas == "XR-VK" ~ preco_medio,
    TRUE ~ NA_real_)) |> 
  arrange(ano, desc(pontas)) |> 
  fill(preco_base, .direction = "down") |> 
  mutate(diff = round((preco_medio - preco_base) / preco_base * 100,1)) |> 
  mutate(manufacturer = fct_recode(manufacturer,
    "TEEJET" = "DEEJET"
  )) -> xr_all

xr_all |> 
  filter(ano == input$select4) |> 
  select(pontas, preco_medio, sd, diff) |> 
  reactable(pagination = FALSE,
              theme = nytimes(font_size = 13, header_font_size = 15),
              resizable = TRUE,
              wrap = TRUE,
            columns = list(
              pontas = colDef(name = "Spray tip", align = "center"), 
              preco_medio = colDef(name = "Price (RS$)", align = "center",
                                   cell = color_tiles(xr_all, colors = 
                                                         c("#FF0000",
                                                           "#7FFFD4"))),
              sd = colDef(name = "SD", align = "center"), 
              diff = colDef(name = "Difference (%)", align = "center",
              cell = data_bars_pos_neg(xr_all, colors = c("#ff3030", "#1e90ff")))))
})
```


## Column {data-width="500"}

```{r}
renderPlotly({
data_cb |> 
  filter(ano == input$select4) |> 
  ggplot(aes(x = fct_reorder(pontas, price), y = price, color = regiao)) +
  geom_boxplot(color = "#333333") +
  geom_jitter(size = 2, alpha = 0.3) +
  coord_flip() +
  labs(color = NULL) +
  scale_color_brewer(palette = "Set1") +
  theme_fivethirtyeight() +
    theme(legend.position = "none")
})
```